---
title: "echofinemap: Getting Started"
author: "<h4>Author: <i>Brian M. Schilder</i></h4>"
date: "<h4>Updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{echofinemap}
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, echo=FALSE, include=FALSE}
pkg <- read.dcf("../DESCRIPTION", fields = "Package")[1]
library(pkg, character.only = TRUE)
```

```R
library(echofinemap)
```

# Quick start: ABF (Approximate Bayes Factor)

ABF is the fastest fine-mapping method because it requires no LD matrix and
no external software. It is a good first pass for identifying credible sets.

```{r abf-example}
## Load bundled example data
dat <- echodata::BST1
LD_matrix <- echodata::BST1_LD_matrix

## Strip any previous fine-mapping columns so we start fresh
dat_clean <- echofinemap::drop_finemap_cols(dat = dat)

## Run ABF
dat_abf <- echofinemap::ABF(dat = dat_clean, verbose = TRUE)
```

Inspect the results -- ABF adds posterior probability columns and a
credible set indicator:

```{r abf-results}
## Key fine-mapping columns added by ABF
abf_cols <- grep("ABF|PP|CS", names(dat_abf), value = TRUE)
print(abf_cols)

## Top SNPs by ABF posterior probability
topsnps <- head(dat_abf[order(-dat_abf$PP),
                         c("SNP","CHR","POS","P","PP","CS")], 10)
print(topsnps)
```

# Full pipeline: `multifinemap()`

`multifinemap()` runs one or more fine-mapping methods in a single call.
The example below runs ABF, SUSIE, and FINEMAP together.

> **Note:** This chunk is set to `eval=FALSE` because SUSIE and FINEMAP
> can be slow and FINEMAP requires an external binary. See the individual
> method help pages for installation instructions.

```{r multifinemap-example, eval=FALSE}
dat_clean <- echofinemap::drop_finemap_cols(dat = echodata::BST1)
LD_matrix <- echodata::BST1_LD_matrix
locus_dir <- file.path(tempdir(), echodata::locus_dir)

dat2 <- echofinemap::multifinemap(
    dat = dat_clean,
    locus_dir = locus_dir,
    LD_matrix = LD_matrix,
    finemap_methods = c("ABF", "SUSIE", "FINEMAP")
)
```

# Session Info

<details>

```{r Session Info}
utils::sessionInfo()
```

</details>
